---
title: "Weight of Fish"
author: "Riley Wheeler"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species =="Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

From this graph I see that the best two predictors of Weight for Perch are Length3 and Height


## Perch

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The one that uses all of the variables

### Best Two regressor model

From the graph, the best two-parameter regression model is based on Length3 and Height.

## Pike

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Pike)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The one that uses all of the variables

### Best Two regressor model

The best models are Length 1 and Length3

## Roach

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The best scenario would be to use all of the variables.

### Best Two regressor model

The Best two models are Length3  and Length1.

## Final Summary Statements
The best overall scenario regardless fo fish is all four variables.

For the Perch, the best scenarios were Length1 and Height  

For Pike The best models are Length 1 and Length3,  

For Roach was Length1 and Length3  
