---
title: "Weight of Fish"
author: "Riley Wheeler"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species =="Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

From this graph I see that the best two predictors of Weight for Perch are Length3 and Height


## Perch

```{r}
pwt = lm(Weight~Length1 + Length2 + Length3 + Height, data=Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ Length1 + Length2 + Length3 + Height, data = Perch, 
             nbest = 2,    # 1best model for each number
             nvmax = NULL, # NULL for no limit on number
             force.in = NULL, force.out = NULL, 
             method = "exhaustive")
regsubsets.out
```


### Best Models

Best model for this case is 

### Best Two regressor model

From the graph, the best two-parameter regressor model is based on Length3 and Height.

## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements